Quantum Magic Games

### 2023-07-04 paper/main.tex
paper => main result second direction

\usepackage{float}
\usepackage{tcolorbox}
\tcbuselibrary{theorems}

\newtcbtheorem{tcbexample}{Example}{
  boxrule=0.15mm,
  colback=gray!15,
  colbacktitle=gray!15,
  coltitle=red!50!black,
  fonttitle=\bfseries,
  detach title,
  before upper={\tcbtitle},
  separator sign none,
  description delimiters={(}{). }
}{ex}

@@

{\renewcommand{\arraystretch}{2}
\begin{figure}
  \centering
  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
      \hhline{---~}
      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
      \\ \hhline{---~}
      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
      \\ \hhline{---~}
      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = \ci{}I \otimes -\ci{}I = I
      \\ \hhline{---~}
      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -\ci{}I \otimes -\ci{}I = -I}
    \end{array}\]
  \caption{Observables used by Alice and Bob to win the Magic Square game.\label{fig:quantum}}
\end{figure}}

@@

  required, \(+1\). Upon receiving Alice's answer, Charlie goes to

@@

>>>>

\usepackage{float}
\usepackage{tcolorbox}
\tcbuselibrary{breakable, skins, theorems}

\newtcbtheorem{tcbexample}{Example}{
  breakable,
  enhanced,
  boxrule=0.15mm,
  colback=gray!15,
  colbacktitle=gray!15,
  coltitle=red!50!black,
  fonttitle=\bfseries,
  detach title,
  before upper={\tcbtitle},
  separator sign none,
  description delimiters={(}{). }
}{ex}

@@

{\renewcommand{\arraystretch}{2}
\begin{figure}[htbp] 
  \centering
  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
      \hhline{---~}
      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
      \\ \hhline{---~}
      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
      \\ \hhline{---~}
      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = \ci{}I \otimes -\ci{}I = I
      \\ \hhline{---~}
      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -\ci{}I \otimes -\ci{}I = -I}
    \end{array}\]
  \caption{Observables used by Alice and Bob to win the Magic Square game.\label{fig:quantum}}
\end{figure}}

@@

  required
  , \(+1\). Upon receiving Alice's answer, Charlie goes to

@@

It remains to show the other direction of the result. That is, the
intersection graph of an arrangement is nonplanar, than the
arrangement is magic.

\begin{proof}
  By the Pontyagin and Kuratowski theorem, everry nonplanar graph contains either
  the \(K_{5}\) or the \(K_{3,3}\) graph as a topological minor. We have already seen
  that the \(K_{3, 3}\) is the intersection graph that corresponds to the magic square
  and that the \(K_{5}\) corresponds to the magic pentagram, and both are magic
  arrangements. Hence, it suffices to demonstrate that, if the intersection graph
  \(G\) of an arrangement has a magic intersection graph \(H\) as a topological minor,
  than \(G\) is magic. For that, we are going to construct a quantum realization
  of \(G\) from the realization of \(H\), as follows:

  \begin{enumerate}
  \item For every vertex in \(H\), assume that the corresponding vertex in
    \(G\) is labelled in the same way.

  \item Assume that the label of every other vertex is \(+1\).

  \item For every edge of \(H\), label each edge of the corresponding  path in \(G\) with
    the same observable.

  \item Label the remaining edges of \(G\) as the identity.
  \end{enumerate}

  To see why items (1) and (2) are safe to assume, recall that an
  arrangement depends only on its parity (meaning that it is possible
  to construct a realization for another arrangement on the same
  vertices and hyperedges, and of same parity), and thus it does not
  matter how you label the vertices of \(G\), as long as its parity
  is \(-1\). It remains to show that the strategy above gives a
  quantum realization of \(G\). For that, we check each of the
  properties of a quantum realization:

  \begin{enumerate}
  \item Every observable \(M\) assigned to a vertex of \(G\) is either one in \(H\) or
    the identity. Hence, \(M\) is Hermitian and squares to the identity.

  \item Every vertex of \(G\) corresponding to a vertex of \(H\) is
    surrounded by the same observables on its edges, plus (possibly)
    copies of the identity. Therefore, these operators mutually
    commute. Furthermore, they multiply to the identity times the
    label of the vertex, which is labelled in the same way as its
    corresponding vertex in \(H\).

  \item Every vertex of \(G\) that lies on a simple path corresponing
    to an edge in \(H\) touches two edges (in and out) labelled with
    the same operator \(M\), which is the operator of the edge in
    \(H\), plus (possibly) copies of the identity. Since
    \(M^{2} = I\), these operators all commute and multiply to
    \(+I\). Recall that we labelled these vertices as \(+1\), as they
    do not have a correspondence in \(H\). Hence, the product of the
    operators multiply to the identity times the vertex's label, as
    desired.

  \item Any other vertex of \(G\) is labelled as \(+1\) and is only
    surrounded by edges labelled as \(+I\), which clearly commute
    and multiply to \(+I\), i.e.\ the identity times the label of the vertex.
  \end{enumerate}
  \qed
\end{proof}
